---
title: 'PSTAT 131: Homework 5'
author: "Lily Li"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(janitor)
library(tidymodels)
library(tidyverse)
library(readr)
pokemon <- read_csv("Pokemon.csv") %>% clean_names()
```
### Q1

clean_names() ensures consistent format and that the names only contain letters, numbers, and underscores. Numbers are appended on duplicate names.

### Q2
```{r}
ggplot(pokemon, aes(y = reorder(factor(type_1), type_1, function(x) length(x)))) +
  geom_bar(fill = "purple") +
  labs(y = "type 1") +
  geom_text(stat = 'count', aes(label = ..count..),position = position_stack(vjust = 0.8))

pokemon %>% count(type_1) # 18 classes

pokemon_clean <- pokemon %>% filter(type_1 %in% c('Bug', 'Fire', 'Grass', 'Normal', 'Water', 'Psychic')) %>%
  mutate(type_1 = factor(type_1), legendary = factor(legendary))
```

Pokemon types with the fewest pokemon in our dataset: FLying(n=4), Fairy(n=17), Ice(n=24).

### Q3
```{r}
set.seed(9)
pokemon_split <- initial_split(pokemon_clean, prop = 0.7, strata = type_1)
train <- training(pokemon_split)
test <- testing(pokemon_split)
dim(train) # 318/458 of observations
dim(test) # 140/458 of observations

set.seed(9)
pokemon_folds <- vfold_cv(train, v = 5, strata = type_1)
```

Stratifying the folds is important since resampling is done seperately for each class; this ensures we have equivalent portions of each type_1 pokemon in each fold and each type_1 class is represented.

### Q4
```{r}
pokemon_recipe <- recipe(type_1 ~ legendary + generation + sp_atk + attack + speed + defense + hp + sp_def, data = pokemon_clean) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_normalize(all_predictors())
```

### Q5
```{r, message=FALSE}
elastic_net_spec <- multinom_reg(penalty = tune(), mixture=0.5) %>% 
  set_mode("classification") %>% 
  set_engine("glmnet") 

workflow <- workflow() %>% 
  add_recipe(pokemon_recipe) %>% 
  add_model(elastic_net_spec)

penalty_grid <- grid_regular(penalty(range = c(-5, 5)), levels = 10)

tune_res <- tune_grid(workflow,
  resamples = pokemon_folds, 
  grid = penalty_grid)
```

5 total models fitted to folds

### Q6
```{r}
autoplot(tune_res)
```

Larger values of penalty and mixture produce better accuracy and ROC AUC.
